Forecasting interrupted time series

### 2023-07-26 fits.qmd
Now compiling

---
title: "Forecasting COVID-affected time series"
author:
- familyname: Rostami-Tabar
  othernames: Bahman
  address:
    - Cardiff Business School
    - Wales CF10 3EU
    - United Kingdom
  email: rostami-tabarb@cardiff.ac.uk
  correspondingauthor: true
- familyname: Hyndman
  othernames: Rob J
  address:
    - Department of Econometrics & Business Statistics
    - Clayton VIC 3800
    - Australia
  email: Rob.Hyndman@monash.edu
abstract: "A brief summary of our ideas"
keywords: "blah, blah"
wpnumber: no/yr
jelcodes: C10,C14,C22
blind: false
cover: false
toc: false
bibliography: references.bib
biblio-style: authoryear-comp
format:
  wp-pdf:
    knitr:
      opts_chunk:
        dev: "CairoPDF"
fig-height: 5
fig-width: 8
keep-tex: true
number-sections: true
cite-method: biblatex
execute:
  echo: false
  warning: false
  message: false
  cache: true
---

@@

```{r}
#| label: forecast
tar_load(fc)
fc <- forecast(fit, h=365)
fc |> filter(Area == "BC", .model=="ets") |> autoplot(df)
fc |> filter(Area == "BC", .model=="stl_ets") |> autoplot(df)
fc |> filter(Area == "BC", .model=="arima") |> autoplot(df)
```

>>>>

---
title: "Forecasting interrupted time series"
author:
- familyname: Rostami-Tabar
  othernames: Bahman
  address:
    - Cardiff Business School
    - Wales CF10 3EU
    - United Kingdom
  email: rostami-tabarb@cardiff.ac.uk
  correspondingauthor: true
- familyname: Hyndman
  othernames: Rob J
  address:
    - Department of Econometrics & Business Statistics
    - Clayton VIC 3800
    - Australia
  email: Rob.Hyndman@monash.edu
abstract: "A brief summary of our ideas"
keywords: "blah, blah"
wpnumber: no/yr
jelcodes: C10,C14,C22
blind: false
cover: false
toc: false
bibliography: references.bib
biblio-style: authoryear-comp
format:
  wp-pdf:
    knitr:
      opts_chunk:
        dev: "CairoPDF"
fig-height: 5
fig-width: 8
keep-tex: true
number-sections: true
cite-method: biblatex
execute:
  echo: false
  warning: false
  message: false
  cache: true
---

@@

```{r}
#| label: forecast
tar_load(fc)
tar_load(df)
fc |> filter(Area == "BC", .model=="ets") |> autoplot(df)
fc |> filter(Area == "BC", .model=="stl_ets") |> autoplot(df)
fc |> filter(Area == "BC", .model=="arima") |> autoplot(df)
```
